### 2018-03-09 Article/Article.tex
09_03_2018

\section*{The model}
Simulations and graphics were performed with the R software (R Development Core Team, 2013). Equations for isoclines and consumption vector slopes were found analytically, as well as stability of equilibrium points. Results were also tested with simulations using Runge-Kutta 4 approximation, from package deSolve \citep{Soetaert2010}.

The model includes $p$ herbivore species competing for $k$ resources embedded into $n$ plant species. For each resource $u$, each herbivore has its own specific requirement, and each plant has %contains 
its own resource availability. These requirements and availabilities are represented by quotas (i.e., quantity of resource per biomass unit). Hence, for an herbivore $i$, the biomass dynamic writes:
\begin{equation}\label{equaherbivoregeneral}
\equa{H_i}= \left ( \mathrm{Min} \left \lbrace \frac{\displaystyle \sum ^n _{j=1} g_{ij} V_j Q_{vjR1}}{Q_{hiR1}}, \ldots,  \frac{\displaystyle \sum ^n _{j=1} g_{ij} V_j Q_{vjRk}}{Q_{hiRk}} \right \rbrace -m_i \right) H_i
\end{equation}
where $H_i$ is herbivore $i$ biomass, $V_j$ is plant $j$ biomass, $g_{ij}$ is consumption rate of plant $j$ by herbivore $i$, $m_i$ is mortality rate of herbivore $i$, $Q_{vjRk}$ is the quota of resource $k$ into plant $j$ biomass (for example: $\text{g }R_k \text{/kg}$ of plant $j$), and $Q_{hiRk}$ is quota of resource $k$ into herbivore $i$ biomass (for example: $\text{g }R_k \text{/kg}$ of herbivore $i$). The ratio between herbivore and plant quotas sets influence of this chemical element on growth limitation for this herbivore. According to Liebig's law of the minimum, the least available resource relative to herbivore requirements is assumed to be growth limiting. \par
Plant biomass is:
\begin{equation}\label{equaplantgeneral}
\equa{V_j}=S_j-a_jV_j-\sum ^p _{i=1} g_{ij}V_jH_i
\end{equation}
where $S_j$ is a function representing the increase of plant biomass (gross supply), $a_j$ is intrinsic loss per capita, such as senescence, the last term on the right represents consumption by herbivores. \par
Resource availability is described as the plant biomass multiplied by the plant quota of the considered element.
\begin{equation} \label{equaresourcegeneral}
R_u=\sum ^n _{j=1} V_jQ_{vjRu}
\end{equation}

@@

\section*{Results}
Resources are provided by several plants, which is a spatial segregation of resources. But each plant provides several resources, which represents a stoichiometric balance issue between plant and herbivore. Spatial segregation and stoichimetric balance will first be studied separately then together.

\subsection*{Spatial segregation of resources}
Consider a limiting resource ($R$). %provided by $n$ plants. 
Herbivores have access to this resource through the consumption of $n$ species of plants, depending on their feeding strategy.   
Resource availability at steady state, for each herbivore, is (see appendix 2 for details):
%At steady state, it is possible to calculate $\barre{R}_{hi}$ for each herbivore $i$ (see appendix 2 for details):
\begin{equation}\label{oneresourcetwoplants}
\barre{R}_{Hi}=\sum ^n _{j=1} \frac{S_j}{a_j+g_{ij}\barre{H}_i}Q_{v1R}
\end{equation}
This $\barre{R}_{Hi}$ represents level of resource remaining available for another herbivore, it also represents the minimal threshold of resource availability for herbivore species $i$ (i.e., if resource availability is below this threshold this herbivore species cannot maintain a population at steady state). Hence, it can be assimilated to Tilman's $R^*$. \par
For simplicity, consider the case where two herbivore species ($H_1$ and $H_2$) compete for one resource ($R$) embedded into two plants species ($V_1$ and $V_2$). Extending equation \ref{oneresourcetwoplants}, resource availabilities for each herbivore species at steady state write:
\begin{equation}
\barre{R}_{H1}=\frac{S_1}{a_1+g_{11}\barre{H}_1}Q_{v1R}+\frac{S_2}{a_2+g_{12}\barre{H}_1}Q_{v2R}
\end{equation}
and
\begin{equation}
\barre{R}_{H2}=\frac{S_1}{a_1+g_{21}\barre{H}_2}Q_{v1R}+\frac{S_2}{a_2+g_{22}\barre{H}_2}Q_{v2R}
\end{equation}
Clearly, the competition outcome is driven by the foraging strategies of the competitors, more specifically, on the efficiencies of their consumption functions ($g_{ij}$). If $g_{11}>g_{21}$ and $g_{12}>g_{22}$, herbivore 1 consumes both plants more efficiently than its competitor. Thus, the competitive exclusion principle holds, and herbivore 2 is excluded. The reverse situation ($g_{11}<g_{21}$ and $g_{12}<g_{22}$) leads to the exclusion of herbivore 1. However, if the two herbivores are specialized on different plant species ($g_{11}>g_{21}$ and $g_{12}<g_{22}$, or  $g_{11}<g_{21}$ and $g_{12}>g_{22}$), coexistence is possible. In other words, despite the fact that herbivores compete for a single resource, the competitive exclusion principle does not necessarily hold. Hence, plants species create a spatial segregation of the resource, and specialization of herbivores on different plant species, similar to niche segregation in space, makes coexistence possible.% because herbivores can overcome the %bottom-up 
%stoichiometric constraint.

@@

Consider $p$ herbivores feeding on one plant species embedding $k$ resources. According to the Liebig's law of the minimum expressed by the minimum function in equation \ref{equaherbivoregeneral}, for each herbivore $i$ the interplay between resource requirement and resource availability will determine which resource is the most limiting for growth \citep{Grover1997}. Depending on their requirements, and on the ratios of resources available in plant biomass, several herbivore species feeding on a single plant species may not be limited by the same resource. %Thus, requirement differences among herbivores can be interpreted as niche segregation. %Yet, as we shall see, this niche segregation does not allow coexistence when two herbivore species feed on a single plant species.\\ 

@@

For a single herbivore $i$, feeding on one plant ($V$), the level of a limiting resource $R_u$ (with $u \in [1,k]$) in plant biomass at equilibrium writes (see appendix 3 for details):

@@

\barre{R}_{uHi}=\barre{V}|_{Ru}\; Q_{vRu} =\frac{m_i}{g_i}Q_{HiRu} 

@@

For simplicity, consider two herbivore species ($H_1$ and $H_2$) competing for two resources ($R_1$ and $R_2$) embedded into a single plant species ($V$). According to equation \ref{resourceoneplant}, the slopes of the ZNGIs only depend on herbivore parameters, which are constant. Therefore, the ZNGIs are parallel to the axis on the phase plan $\{R_1,R_2\}$. %According to the classical resource-ratio theory \citep{Tilman1982}, 

@@

A second necessary condition relies on the difference between the slopes of the consumption vectors of the competitors \citep{Tilman1982}.  The consumption vectors graphically illustrate how resource consumption drives the levels of resources from resource supply to equilibrium levels. In the phase plan, resource supply is represented by the supply point $S$, which is the total amount of resources at equilibrium in absence of consumption:

\begin{equation}
S_{R_1}=Q_{vR_1}(S-a\barre{V})
\end{equation}
\begin{equation}
S_{R_2}=Q_{vR_2}(S-a\barre{V})
\end{equation}
For a given herbivore $i$, the consumption vector $\vec{C_i}$ writes:
\begin{equation}
\vec{C_i}=\left( 
\begin{array}{l}
g_i\barre{V}\barre{H}_i Q_{vR_1}\\
g_i\barre{V}\barre{H}_i Q_{vR_2}
\end{array}\right) 
=g_i\barre{V}\barre{H}_i \left( 
\begin{array}{l}
Q_{vR_1}\\
Q_{vR_2}
\end{array}\right) 
\end{equation}
The vectorÕs slope is determined by the ratios of resources embedded in plant biomass. An important consequence is that all herbivores have the same slope of consumption vector when feeding on a single plant. This constraint precludes coexistence, and the resource-ratio embedded in plant biomass determines which of the competitor will displace the other (figure \ref{herbifig}). %Hence, despite niche segregation on the requirement axe, two herbivores cannot coexist on two resources. 
Hence, despite differences in requirement, two herbivores cannot coexist on several resources.
This result is in contrast with the classical resource-ratio theory, which stipulates that two consumer may coexist on two resources under certain conditions. The reason is that classically, consumers are assumed to control the slope of their consumption vector \citep{Tilman1982}. This assumption is valid for primary producers, which take up essential nutrients independently in their environment, in the form of dissolved chemical molecules, but not for herbivores, which take up essential nutrients already bounded in plant biomass. Therefore, %niche segregation alone cannot promote coexistence. Only 
only the herbivore that can match plant stoichiometry the best can persist and outcompete other herbivores. This leads to a strong bottom-up stoichiometric constraint. 
\par

@@

In this section, we present the general case of the model, where herbivores compete for multiple resources embedded into multiple plants. Assuming that nutrient quotas differ among plant species, the consumption of a given plant is not equivalent to consumption of another plant. Due to spatial segregation among resources, herbivores may control their diet by allocating more time/energy to feed on specific plants rather than others. Therefore, each herbivore may find a specific pathway to collect resources \citep{Simpson1995, Raubenheimer1999}. The foraging strategy of a given herbivore is graphically represented by the consumption vector, which is the combination of the consumption vectors for all the plant species consumed. As a consequence, the slope of the consumption vector depends on the foraging strategy of the herbivore, which can adjust the slope by consuming more efficiently a given species versus the others. Thus, niche segregation among herbivore species is a combination of spatial segregation and segregation on the requirements. As we shall see, this niche segregation allows for coexistence of multiple herbivores on multiple resources. \par
To simplify, we consider here the case of two herbivores competing for two plants embedding two resources (see appendix 4 for details). The resource supply is represented in the phase plan by the supply point S, which is the total amount of resources at equilibrium in plants 1 and 2, in absence of consumption:
\begin{equation}
S_{R1}=Q_{v1R1}(S_{v1}-a\barre{V}_1)+Q_{v2R1}(S_{v2}-a\barre{V}_2)
\end{equation}
\begin{equation}
S_{R2}=Q_{v1R2}(S_{v1}-a\barre{V}_1)+Q_{v2R2}(S_{v2}-a\barre{V}_2)
\end{equation}
For a given herbivore $i$, the ZNGI slope ($\alpha|_{Ru}$) for each resource ($R_u$) is:
\begin{equation}\label{alpha}
\alpha|_{Ru}=\frac{\barre{V}_1|_{Ru}Q_{v1R2}+\barre{V}_2|_{Ru}Q_{v2R2}}{\barre{V}_1|_{Ru}Q_{v1R1}+\barre{V}_2|_{Ru}Q_{v2R1}}
\end{equation}
Note that the slope depends on $\{ \barre{V}_1,\barre{V}_2\}$, which themselves depend both on the herbivore and the plant parameters (including the supply parameters). Hence, the ZNGI slope is not parallel to the axis. \par

However, it is possible to define boundary ZNGI. Considering that herbivore $i$ can consume both plants, its foraging strategy will lie between exclusive consumption of plant 1, on one side, and exclusive consumption of plant 2, on the other side. Thus, boundary ZNGI slope writes (see appendix 4 for details):
\begin{equation}\label{boundaryZNGI}
\barre{R}_u=\frac{Q_{hiRu}m_i}{g_{ij}}
\end{equation}
This isocline $\barre{R}_u$ represents the ZNGI in the case where herbivore $i$ consumes only plant $j$ and is limited by nutrient $u$. In case of two plants consumed, the real $\barre{R}_u$ will lie between two boundary ZNGI (one for each plant).

By looking at boundary ZNGI equation (\ref{boundaryZNGI}), it appears that ZNGI slopes depend only on herbivore constant parameters. Therefore, it is parallel to the axis. Moreover, two herbivores having similar quotas but different feeding strategies would have different ZNGI. Thus, if boundary ZNGI of two herbivores cross each other, coexistence might be possible. \par

Next, competition outcome will depend on the relative orientation of the consumption vector of herbivores \citep{Tilman1980}. However, vector slope calculation is uneasy in the case of packaged resources because vector slope depends on plant supply points. Hence, for a given herbivore, vectors do not have a constant slope valid for all supply conditions. This is why instead of consumption vectors, the model allows the calculation of boundary vectors that determine an area in the phase plan where each herbivore species could coexist with an other one. It is possible to determine a boundary relation between plant supply points ($S_1$ and $S_2$) that allows each herbivore to consume both resources when one resource is limiting, and leads to $\barre{V}_1$ and $\barre{V}_2$ at steady state. These boundary supply points are $S_{1hi}$ and $S_{2hi}$ for plant 1 and 2 respectively (see appendix 4). Hence, boundary vector slopes are:
\begin{equation}
\vec{C}_{h1}= 
\begin{pmatrix}
\barre{S}_{1h1} \;Q_{v1R1}+\barre{S}_{2h1}\; Q_{v2R1} \\
\barre{S}_{1h1}\; Q_{v1R2}+\barre{S}_{2h1}\; Q_{v2R2} \\
\end{pmatrix} 
\end{equation}
\begin{equation}
\vec{C}_{h2}= 
\begin{pmatrix}
\barre{S}_{1h2} \;Q_{v1R1}+\barre{S}_{2h2}\; Q_{v2R1} \\
\barre{S}_{1h2}\; Q_{v1R2}+\barre{S}_{2h2}\; Q_{v2R2} \\
\end{pmatrix} 
\end{equation}
These two boundary vectors play a similar role as consumption vectors in Tilman's model. However, as resources are packaged into plants, vector slopes depend on the way herbivore species feed on plants containing resources.  
Hence, assuming plant 1 is richer in resource 1 ($Q_{v1R1}>Q_{v2R1}$), and plant 2 is richer in resource 2 ($Q_{v1R2}<Q_{v2R2}$), and assuming herbivore 1 is more limited by resource 1 ($Q_{h1R1}>Q_{h1R2}$), and herbivore 2 is more limited by resource 2 ($Q_{h2R1}<Q_{h2R2}$), two general strategies can be considered. The first one occurs when each herbivore species consumes preferentially the plant species which gives the greater quantity of the most limiting resource for this herbivore species, and which is less limiting for its competitor (i.e., $g_{11}>g_{12}$ and $g_{21}<g_{22}$). In that case, if we consider the boundary vectors for herbivore 1 and for herbivore 2, we can define several zones on the phase plan (see figure \ref{Coexistence}). The zone between the two boundary vectors represents the supply conditions allowing stable coexistence of the two herbivore species. Thus, each herbivore consumes the most profitable plant (i.e., quotas and consumption functions follow a similar trend), but each herbivore is specialized (more or less) on a different plant than its competitor, which promotes coexistence. \par
The second case represents the reverse situation, where each herbivore species consumes preferentially the plant species which provides greater quantity of the most limiting resource for its competitor (i.e., $g_{11}<g_{12}$ and $g_{21}>g_{22}$). Hence, the zone between the boundary vectors does not allow coexistence (see figure \ref{Exclusion}), and in many cases equation \ref{Systeme} does not have any realistic solution (with both herbivore species persisting). Thus, competitive exclusion is the general outcome. \par

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm,keepaspectratio]{1plant} 
\caption{Phase plan with two herbivore species feeding on one plant species. Black lines are herbivore 1 ZNGI, dotted lines are herbivore 2 ZNGI, and grey arrow is the common consumption vector. Interpretations are quite similar with those from Tilman's model \citep{Tilman1982}. Roman numbers represent different zones for supply point position. Zone I and zone V do not provide sufficient amounts in $R_1$ and $R_2$ respectively. None herbivore species can live in these conditions. Zone II contains enough quantities of $R_1$ for herbivore 1, but not for herbivore 2. Zone III potentially has enough quantities of both resources for both herbivore species. In zone IV, only herbivore 2 can survive because there is not enough $R_2$ for herbivore 1. Supply point represents total amount of resources due to plant biomass rebuilding. Both herbivore species sample resources through the same consumption vector. In this exemple, the trajectory cross herbivore 2 ZNGY first and then herbivore 1 ZNGI. The crossing point with herbivore 1 ZNGI becomes an equilibrium point (E). Herbivore 1 is limited by $R_2$. Herbivore 2 is excluded.}
\label{herbifig}
\end{figure}

>>>>

\section*{The model}
Simulations and graphics were performed with the R software (R Development Core Team, 2017). Equations for isoclines and consumption vector slopes were found analytically, as well as stability of equilibrium points. Results were also tested with simulations using Runge-Kutta 4 approximation, from package deSolve \citep{Soetaert2010}.

The model includes $p$ herbivore species competing for $k$ resources embedded into $n$ plant species. For each resource $u$, each herbivore has its own specific requirement, and each plant has %contains 
its own resource availability. These requirements and availabilities are represented by quotas (i.e., quantity of resource per biomass unit). Hence, for an herbivore $i$, the biomass dynamic writes:
\begin{equation}\label{equaherbivoregeneral}
\equa{H_i}=  \mathrm{Min} \left \lbrace \frac{\displaystyle \sum ^n _{j=1} g_{ij} V_j Q_{vjR1}}{Q_{hiR1}}, \ldots,  \frac{\displaystyle \sum ^n _{j=1} g_{ij} V_j Q_{vjRk}}{Q_{hiRk}} \right \rbrace H_i -m_i H_i
\end{equation}
where $H_i$ is herbivore $i$ biomass, $V_j$ is plant $j$ biomass, $g_{ij}$ is consumption rate of plant $j$ by herbivore $i$, $m_i$ is mortality rate of herbivore $i$, $Q_{vjRk}$ is the quota of resource $k$ into plant $j$ biomass (for example: $\text{g }R_k \text{/kg}$ of plant $j$), and $Q_{hiRk}$ is quota of resource $k$ into herbivore $i$ biomass (for example: $\text{g }R_k \text{/kg}$ of herbivore $i$). The ratio between herbivore and plant quotas for a given resource represents how this chemical element limits the growth of this herbivore. According to Liebig's law of the minimum, the least available resource relative to herbivore requirements (over the $k$ resources) is assumed to be growth limiting. \par
Plant biomass is:
\begin{equation}\label{equaplantgeneral}
\equa{V_j}=S_j-a_jV_j-\sum ^p _{i=1} g_{ij}V_jH_i
\end{equation}
where $S_j$ is a function representing the increase of plant biomass (gross supply), $a_j$ is intrinsic loss per capita, such as senescence, the last term on the right represents consumption by herbivores. \par
Resource availability is described as the plant biomass multiplied by the plant quota of the considered element.
\begin{equation} \label{equaresourcegeneral}
R_u=\sum ^n _{j=1} V_jQ_{vjRu}
\end{equation}

@@

\section*{Results}
Resources are provided by several plants that may be consumed differently, which represents a spatial segregation of resources. But each plant provides several resources; thus, the stoichiometric balance of resources also plays a role. %which represents a stoichiometric balance issue between plants and herbivores. 
Spatial segregation and stoichimetric balance will first be studied separately, then together.

\subsection*{Spatial segregation of resources}
Let's consider a limiting resource ($R$). %provided by $n$ plants. 
Herbivores have access to this resource through the consumption of $n$ species of plants, depending on their respective feeding strategy.   
Resource availability at steady state, for each herbivore, is (see appendix 1 for details):
%At steady state, it is possible to calculate $\barre{R}_{hi}$ for each herbivore $i$ (see appendix 2 for details):
\begin{equation}\label{oneresourcetwoplants}
\barre{R}_{Hi}=\sum ^n _{j=1} \frac{S_j}{a_j+g_{ij}\barre{H}_i}Q_{VjR}
\end{equation}
%This 
$\barre{R}_{Hi}$ represents the level of resource remaining available for another herbivore, it also represents the minimal threshold of resource availability for herbivore species $i$ (i.e., if resource availability is below this threshold this herbivore species cannot maintain a population at steady state). Hence, it can be assimilated to Tilman's $R^*$. \par
For simplicity, consider the case where two herbivore species ($H_1$ and $H_2$) compete for one resource ($R$) embedded into two plants species ($V_1$ and $V_2$). Extending equation \ref{oneresourcetwoplants}, resource availabilities for each herbivore species at steady state write:
\begin{equation}
\barre{R}_{H1}=\frac{S_1}{a_1+g_{11}\barre{H}_1}Q_{V1R}+\frac{S_2}{a_2+g_{12}\barre{H}_1}Q_{V2R}
\end{equation}
and
\begin{equation}
\barre{R}_{H2}=\frac{S_1}{a_1+g_{21}\barre{H}_2}Q_{V1R}+\frac{S_2}{a_2+g_{22}\barre{H}_2}Q_{V2R}
\end{equation}
Clearly, the competition outcome is driven by the foraging strategies of the competitors, more specifically, on the efficiencies of their consumption functions ($g_{ij}$). If $g_{11}>g_{21}$ and $g_{12}>g_{22}$, herbivore 1 consumes both plants more efficiently than its competitor. Thus, the competitive exclusion principle holds, and herbivore 2 is excluded. The reverse situation ($g_{11}<g_{21}$ and $g_{12}<g_{22}$) leads to the exclusion of herbivore 1. However, if the two herbivores are specialized on different plant species ($g_{11}>g_{21}$ and $g_{12}<g_{22}$, or  $g_{11}<g_{21}$ and $g_{12}>g_{22}$), coexistence is possible. In other words, despite the fact that herbivores compete for a single resource, the competitive exclusion principle does not necessarily hold. Hence, plants species create a spatial segregation of the resource, and specialization of herbivores on different plant species, similar to niche segregation in space, makes coexistence possible.% because herbivores can overcome the %bottom-up 
%stoichiometric constraint.

@@

Consider $p$ herbivores feeding on one plant species embedding $k$ resources. According to the Liebig's law of the minimum expressed by the minimum function in equation \ref{equaherbivoregeneral}, for each herbivore $i$ the interplay between resource requirement and resource availability will determine which resource is the most limiting for growth \citep{Grover1997}. Depending on herbivore requirements, and ratios of resources available in plant biomass, several herbivore species feeding on a single plant species may not be limited by the same resource. %Thus, requirement differences among herbivores can be interpreted as niche segregation. %Yet, as we shall see, this niche segregation does not allow coexistence when two herbivore species feed on a single plant species.\\ 

@@

For a single herbivore $i$, feeding on one plant ($V$), the level of a limiting resource $R_u$ %(with $u \in [1,k]$) 
in plant biomass at equilibrium writes (see appendix 2 for details):

@@

\barre{R}_{uHi}=\barre{V}|_{Ru}\; Q_{VRu} =\frac{m_i}{g_i}Q_{HiRu} 

@@

For simplicity, consider two herbivore species ($H_1$ and $H_2$) competing for two resources ($R_1$ and $R_2$) embedded into a single plant species ($V$). According to equation \ref{resourceoneplant}, the slopes of the ZNGIs only depend on herbivore parameters, which are constant (for a given herbivore). Therefore, the ZNGIs are parallel to the axis on the phase plan $\{R_1,R_2\}$. %According to the classical resource-ratio theory \citep{Tilman1982}, 

@@

A second necessary condition relies on the slopes of the consumption vectors of the competitors %the difference between the slopes of the consumption vectors of the competitors 
\citep{Tilman1982}.  The consumption vectors graphically illustrate how resource consumption drives the levels of resources from resource supply to equilibrium levels. In the phase plan, resource supply is represented by the supply point $S$, which is the total amount of resources at equilibrium in absence of consumption:

\begin{equation}
S_{R_1}=Q_{VR_1}(S-a\barre{V})
\end{equation}
\begin{equation}
S_{R_2}=Q_{VR_2}(S-a\barre{V})
\end{equation}
%For a given herbivore $i$, the consumption vector $\vec{C_i}$ writes:
A given herbivore $i$ consumes resource $R_1$ at a rate $g_i\barre{V}\barre{H}_i Q_{VR_1}$ and resource $R_2$ at a rate $g_i\barre{V}\barre{H}_i Q_{VR_2}$. Thus, 
the consumption vector $\vec{C_i}$ writes: 
\begin{equation}
\vec{C_i}=\left( 
\begin{array}{l}
g_i\barre{V}\barre{H}_i Q_{VR_1}\\
g_i\barre{V}\barre{H}_i Q_{VR_2}
\end{array}\right) 
=g_i\barre{V}\barre{H}_i \left( 
\begin{array}{l}
Q_{VR_1}\\
Q_{VR_2}
\end{array}\right) 
\end{equation}
%The vector's slope 
It appears that the slope of its consumption vector is determined by the ratios of resources embedded in plant biomass. An important consequence is that all herbivores have the same slope for their consumption vector when feeding on a single plant species. This constraint precludes coexistence, and the resource-ratio embedded in plant biomass determines which of the competitors will displace the other (figure \ref{herbifig}). %Hence, despite niche segregation on the requirement axe, two herbivores cannot coexist on two resources. 
Since herbivore respective requirements are located along a gradient of resource ratios ($R_1 / R_2$), the one that shows a ratio closer to the plant ratio than any other one will outcompete other herbivore species. Hence, despite differences in requirements, two herbivores cannot coexist on several resources.  %Plant resource ratios determine the outcome of competition between herbivores, which is a bottom-up stoichiometry.   
\par
This result is in contrast with the classical resource-ratio theory, which stipulates that two consumers may coexist on two resources under certain conditions. The reason is that classically, consumers are assumed to control the slope of their consumption vector \citep{Tilman1982}. This assumption is valid for primary producers, which take up essential nutrients independently in their environment, in the form of dissolved chemical molecules, but not for herbivores, which take up essential nutrients already bounded in plant biomass. Therefore, %niche segregation alone cannot promote coexistence. Only 
only the herbivore that can match plant stoichiometry the best can persist and outcompete other herbivores. Plant resource ratios determine the outcome of competition between herbivores, which is a bottom-up stoichiometric constraint. 
%This leads to a strong bottom-up stoichiometric constraint. 
\par

@@

In this section, we present the general case of the model, where herbivores compete for multiple resources embedded into multiple plants (i.e., spatial segregation of resources and bottom-up stoichiometry play a role). Assuming that nutrient quotas differ among plant species, the consumption of a given plant is not equivalent to consumption of another plant. Due to spatial segregation among resources, herbivores may control their diet by allocating more time/energy to feed on specific plants rather than others. Therefore, each herbivore may find a specific pathway to collect resources \citep{Simpson1995, Raubenheimer1999}. The foraging strategy of a given herbivore is graphically represented by the consumption vector, which is the combination of the consumption vectors for all plant species consumed. %As a consequence, the slope of the consumption vector depends on the foraging strategy of the herbivore, which can adjust the slope by consuming more efficiently a given species versus the others. 
By consuming more efficiently a given species than others, an herbivore can control the slope of its consumption vector. 
%Thus, niche segregation among herbivore species is a combination of spatial segregation and segregation on the requirements. As we shall see, this niche segregation allows for coexistence of multiple herbivores on multiple resources. 
\par
To simplify, we consider here the case of two herbivores competing for two plants embedding two resources. %(see appendix 3 for details). 
These two herbivores will coexist only if they are not limited by the same resource. Let's consider the case where herbivore 1 is mostly limited by resource 1, and herbivore 2 is mostly limited by resource 2. The resource supply is represented in the phase plan by the supply point $S$, which is the total amount of resources at equilibrium in plants 1 and 2, in the absence of consumption:
\begin{equation}
S_{R1}=Q_{V1R1}(S_{V1}-a\barre{V}_1)+Q_{V2R1}(S_{V2}-a\barre{V}_2)
\end{equation}
\begin{equation}
S_{R2}=Q_{V1R2}(S_{V1}-a\barre{V}_1)+Q_{V2R2}(S_{V2}-a\barre{V}_2)
\end{equation}
For a given herbivore $i$, the ZNGI slopes ($\alpha|_{R1}$ and $\alpha|_{R2}$) for each resource (when $R_1$ and $R_2$ are limiting respectively) write:
\begin{equation}\label{alpha}
\alpha|_{R1}=\frac{\barre{V}_1|_{R1}Q_{V1R2}+\barre{V}_2|_{R1}Q_{V2R2}}{\barre{V}_1|_{R1}Q_{V1R1}+\barre{V}_2|_{R1}Q_{V2R1}}
\end{equation}
\begin{equation}\label{alpha}
\alpha|_{R2}=\frac{\barre{V}_1|_{R2}Q_{V1R2}+\barre{V}_2|_{R2}Q_{V2R2}}{\barre{V}_1|_{R2}Q_{V1R1}+\barre{V}_2|_{R2}Q_{V2R1}}
\end{equation}
Note that the slopes depend on $\barre{V}_1$ and $\barre{V}_2$, which themselves depend both on the herbivore and the plant parameters (including the supply parameters). Hence, ZNGIs are not parallel to the axis. \par

However, it is possible to define boundary ZNGIs. Considering that herbivore $i$ can consume both plants, its foraging strategy will lie between exclusive consumption of plant 1, on one side, and exclusive consumption of plant 2, on the other side. Thus, boundary ZNGI slopes write (see appendix 3 for details):
\begin{equation}\label{boundaryZNGI1}
\barre{R}_1=\frac{m_i}{g_{ij}}Q_{HiR1}
\begin{equation}\label{boundaryZNGI2}
\barre{R}_2=\frac{m_i}{g_{ij}}Q_{HiR2}
These isoclines $\barre{R}_1$ and $\barre{R}_2$ represent the ZNGIs in the case where herbivore $i$ consumes only plant $j$ and is limited by $R_1$ (eq. \ref{boundaryZNGI1}) or $R_2$ (eq. \ref{boundaryZNGI2}). In case of two plants consumed, the real $\barre{R}_1$ and $\barre{R}_2$ will lie between two boundary ZNGIs, one for each plant (see fig. 3).
%By looking at boundary ZNGI (eq. \ref{boundaryZNGI1} and \ref{boundaryZNGI2}), 
It appears that ZNGI slopes depend only on herbivore constant parameters. Therefore, boundary ZNGIs are parallel to the axis. Moreover, two herbivores having similar quotas but different feeding strategies would have different ZNGIs. Thus, if boundary ZNGIs of two herbivores cross each other, coexistence might be possible. Determining existence of an equilibrium point is possible by solving the following system (see appendix 3 for details):
\begin{equation} \label{systemmaintext}
\begin{cases}
g_{11}\barre{V}_1 Q_{V1R1}+g_{12}\barre{V}_2 Q_{V2R1}=m_1 Q_{H1R1} \\
g_{21}\barre{V}_1 Q_{V1R2}+g_{22}\barre{V}_2 Q_{V2R2}=m_2 Q_{H2R2}
\end{cases} 
where $\barre{V}_1$ and $\barre{V}_2$ are biomass at equilibrium for plant 1 and 2 respectively. If system \ref{systemmaintext} leads to a realistic equilibrium point (plant biomasses and herbivores biomasses are all positive), then an equilibrium point exists. 
Next, competition outcome will depend on the relative orientation of the consumption vector of herbivores \citep{Tilman1980}. For a given herbivore, the consumption vector slope writes:
\begin{equation}
\vec{C}_{Hi}= \barre{H}_i
\begin{pmatrix}
g_{i1}\barre{V}_1Q_{V1R1}+g_{i2}\barre{V}_2Q_{V2R1} \\
g_{i1}\barre{V}_1Q_{V1R2}+g_{i2}\barre{V}_2Q_{V2R2} \\
\end{pmatrix} 
It appears that this vector slope depends on $\barre{V}_1$ and $\barre{V}_2$, which themselves varies with plant supply points ($S_1$ and $S_2$). 
%However, vector slope calculation is uneasy in the case of packaged resources because vector slope depends on plant supply points. 
Hence, for a given herbivore in the case of packaged resources, vectors do not have a constant slope valid for all supply conditions. This is why instead of consumption vectors, the model allows the calculation of boundary vectors that determine an area in the phase plan where each herbivore species could coexist with the other one. 
It is possible to determine a boundary relation between plant supply points ($S_1$ and $S_2$) that allows each herbivore $i$ to consume both resources when one resource is limiting, and leads to $\barre{V}_1$ and $\barre{V}_2$ at steady state. These boundary supply points are $\barre{S}_{1Hi}$ and $\barre{S}_{2Hi}$ for plant 1 and 2 respectively consumed by herbivore $i$ (see appendix 3 for details). 
\begin{equation}\label{supplymaintext}
\barre{S}_{2Hi}=(\barre{S}_{1Hi}-a_1)\frac{g_{i2}\barre{V}_2}{g_{i1}\barre{V}_1}+a_2\barre{V}_2
Hence, boundary vector slopes are:
\begin{equation}
\vec{C}_{H1}= 
\begin{pmatrix}
\barre{S}_{1H1} \;Q_{V1R1}+\barre{S}_{2H1}\; Q_{V2R1} \\
\barre{S}_{1H1}\; Q_{V1R2}+\barre{S}_{2H1}\; Q_{V2R2} \\
\end{pmatrix} 
\begin{equation}
\vec{C}_{H2}= 
\begin{pmatrix}
\barre{S}_{1H2} \;Q_{V1R1}+\barre{S}_{2H2}\; Q_{V2R1} \\
\barre{S}_{1H2}\; Q_{V1R2}+\barre{S}_{2H2}\; Q_{V2R2} \\
\end{pmatrix} 
These two boundary vectors play a similar role as consumption vectors in Tilman's model. However, as resources are packaged into plants, vector slopes depend on the way herbivore species feed on plants containing resources (eq. \ref{supplymaintext}).  
Hence, assuming plant 1 is richer in resource 1 ($Q_{V1R1}>Q_{V2R1}$), and plant 2 is richer in resource 2 ($Q_{V1R2}<Q_{V2R2}$), and assuming herbivore 1 is more limited by resource 1 ($Q_{H1R1}>Q_{H1R2}$), and herbivore 2 is more limited by resource 2 ($Q_{H2R1}<Q_{H2R2}$), two general strategies can be considered. The first one occurs when each herbivore species consumes preferentially the plant species which gives the greater quantity of the most limiting resource for this herbivore species, and which is less limiting for its competitor (i.e., $g_{11}>g_{12}$ and $g_{21}<g_{22}$). In that case, if we consider the boundary vectors for herbivore 1 and for herbivore 2, we can define several zones on the phase plan (see figure \ref{Coexistence}). The zone between the two boundary vectors represents the supply conditions allowing stable coexistence of the two herbivore species. Thus, each herbivore consumes the most profitable plant (i.e., quotas and consumption functions follow a similar trend), but each herbivore is specialized (more or less) on a different plant than its competitor, which promotes coexistence. 
The second case represents the reverse situation, where each herbivore species consumes preferentially the plant species which provides greater quantity of the most limiting resource for its competitor (i.e., $g_{11}<g_{12}$ and $g_{21}>g_{22}$). Hence, the zone between the boundary vectors does not allow coexistence (see fig.  \ref{Exclusion}), and in many cases system \ref{systemmaintext} does not have any realistic solution (with both herbivore species persisting). Thus, competitive exclusion is the general outcome. 

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm,keepaspectratio]{1plant} 
\caption{Phase plan with two herbivore species feeding on one plant species. Black solid lines are herbivore 1 ZNGI, dotted lines are herbivore 2 ZNGI, and grey arrow is the common consumption vector. Interpretations are quite similar with those from Tilman's model \citep{Tilman1982}. Roman numbers represent different zones for supply point position. Zone I and zone V do not provide sufficient amounts in $R_1$ and $R_2$ respectively. None herbivore species can live in these conditions. Zone II contains enough quantities of $R_1$ for herbivore 1, but not for herbivore 2. Zone III potentially has enough quantities of both resources for both herbivore species. In zone IV, only herbivore 2 can survive because there is not enough $R_2$ for herbivore 1. Supply point represents total amount of resources due to plant biomass rebuilding. Both herbivore species sample resources through the same consumption vector. In this exemple, the trajectory cross herbivore 2 ZNGY first and then herbivore 1 ZNGI. The crossing point with herbivore 1 ZNGI becomes an equilibrium point (E). Herbivore 1 is limited by $R_2$. Herbivore 2 is excluded.}
\label{herbifig}
\end{figure}
